Verifying Concurrent Search Structure Templates for C Programs using VST

### 2023-04-05 concurrency/CONCUR 2023/paper.tex
add more about give-up

>>>>

\begin{lstlisting}[language = C, backgroundcolor=\color{white},   
	commentstyle=\color{codegreen},
	basicstyle=\ttfamily\footnotesize,
	breakatwhitespace=false,  breaklines=true,  keepspaces=true,                                
	showspaces=false,  showstringspaces=false,
	showtabs=false, tabsize=1]
	typedef struct tree_t {tree *t; lock_t *lock; int min; int max;} tree_t;
\end{lstlisting}

%% C implementation 
To implement the template algorithm, it is crucial to keep track of the lower and upper bounds of the keys present in the subtree rooted at the current node. Therefore, we have incorporated two new fields, \lstinline{min} and \lstinline{max}, into each node of type \lstinline{tree_t} in our C implementation. These fields respectively store the lower and upper bounds of the keys. When a thread arrives at a node in search of $x$, it check if $x$ falls within the range of that node.
